### 2023-05-17 application.tex
up

\alain{c'est la preuve de quoi en dessous ?}
\begin{proof}
Consider a given $k \in \N$.
Consider $\Bad \subseteq \N^d$ upward-closed and $\Safe \subseteq \N^d$ downward-closed.
Consider a given vector addition system $V$, \alain{bizarre de dire ça "which has a finite number of transitions."}
Let us call $c_{\max}$ the maximal absolute value of a constant appearing in a coordinate of a transition of $V$.

>>>>

\begin{proof}
Consider a given $k \in \N$,
 $\Bad \subseteq \N^d$ upward-closed and $\Safe \subseteq \N^d$ downward-closed, and
consider a given vector addition system $V$.
Let us call $c_{\max}$ the maximal absolute value of a constant appearing in a coordinate of a transition of $V$.
